Topic 21: AUG experiment KoM

### 2017-03-03 Meetings/KoM02March17/kom_020317_madsen_vianello.tex
update to KoM presentation with clarification for the current scan

@@

    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference
        (0.8 MA). Reduce current to 0.6 MA
      keeping the same toroidal field $B_{\phi}$ adjust the fueling

@@

    \item \textcolor{ta3chameleon}{Repeat shot \#1 changing
        the toroidal field in order to match the same $q_{95}$ as reference
      (\emph{Current scan at fixed $q_{95}$}). We can adjust the
      current level in order to match the request for operation with
      B$_{t} = 2$T (Alves)}
    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA
        adjusting the fueling rate and keeping the same toroidal field
      as reference}
    \item \textcolor{ta3chameleon}{Repeat \# 3 keeping the same
        $q_{95}$ as reference shot}

@@

\end{frame}
\begin{frame}{Required diagnostic and analysis}
    \item[$\boxtimes$] Midplane Manipulator
    \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
        available simultaneously}
    \item[$\square$] RFA \#2
    \item[$\square$] Divertor probes
    \item[$\boxtimes$] Neutral profiles
    \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
      infrared measurements available/useful?}
    \item[$\square$] GPI
    \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
      obtained during the q$_{95}$ scan}
    \item[$\boxtimes$] Fast probes on the limiter
    \item[$\square$] Bolometer/AXUV in the divertor region
\end{frame}

>>>>

We choose are reference shot \# 30269 (I$_p$ = 0.8 MA, B$_{\phi}$ = 2.5T, q$_{95}\approx 4.5$)

@@

    \item \textcolor{ta3chameleon}{Shot at I$_p$=0.6 MA
      keeping the same toroidal field $B_{\phi}$ = 2.5T as the reference adjust the fueling

@@

  \item \textcolor{ta3chameleon}{Shot at I$_p$ = 0.6MA
      reduce the toroidal field B$_{\phi}\approx $2T in order to match q$_{95}\approx 4.5$, 
      (\emph{Current scan at fixed $q_{95}$}). This would accommodate
      the diagnostic request of D. Aguiam}
    \item \textcolor{ta3chameleon}{Density ramp with I$_p$ = 1MA and
        B$_{\phi}$ = 2.5T}
    \item \textcolor{ta3chameleon}{Density ramp with I$_{p}$ = 1MA,
        increasing the toroidal field in order to match q$_{95}\approx
        4.5$}

@@

   \item \textcolor{ta3skyblue}{Given that the upper divertor is less
       diagnosed then the lower one we prefer eventually to operate
       with reverse B$_{\phi}$}

\end{enumerate}
  }
\end{frame}
\begin{frame}{Required diagnostic and analysis}
  \begin{itemize}
    \item[$\boxtimes$] Midplane Manipulator
    \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
        available simultaneously}
    \item[$\square$] RFA \#2
    \item[$\square$] Divertor probes
    \item[$\boxtimes$] Neutral profiles
    \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
      infrared measurements available/useful?}
    \item[$\square$] GPI
    \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
      obtained during the q$_{95}$ scan}
    \item[$\boxtimes$] Fast probes on the limiter
    \item[$\square$] Bolometer/AXUV in the divertor region
  \end{itemize}
\end{frame}
